Failure Behaviour Analysis of Automated Pond Oxygen Management System

### 2015-02-19 IFIP FTA/manuscript.tex
reltaed work

>>>>

\textbf{FTA has been widely used in different area in ordre to .....
US aerospace and missile programs have been proposed a new Methods to perform risk and reliability assessment in the early 1960s [NASA Office]. FTA an analysis has been used on Clinical work-flows to ensure the safety of these high-risk workflows [lamis]. The fault tree for pressure tank analysis has been proposed in [NASA Office of Safety and Mission Assurance].
Elctornics system has used the FTA to study the behaviour of electronics system. Authors in [Microelectronics Reliability] uses FTA on printed circuit board assembly and 
for assessment of power system reliability [Reliability Engineering  System Safety]. The industrial systems are the crucial point of failure analysis, software fault tree analysis for product lines has been proposed in  [High Assurance Systems Engineering]. The biological system uses the FTA to analysis the failure of biomedical operation such as Analysis for Biological Invasions  [Biological Invasions].}
